The SMT Competition 2015--2018

### 2018-11-20 2018/report/SMT-COMP.tex
Minor, references, table for competition-wide ranking

For space reasons, the discussion in this paper is necessarily
limited.  Complete data about past competitions since 2015 (and partly
for earlier competitions) is available from the competition web site,
\url{http://www.smtcomp.org}.  This includes detailed results for each
solver/benchmark combination, totaling nearly 6 million data records
(about 1.1~GB in CSV format).

@@

The competition is organized under the direction of the SMT Steering
Committee, which appoints the competition chair.  (This appointment
should happen ``within 30 days from the end of the current edition of
the SMT workshop''~\cite{smt-bylaws} but in practice has often
happened later.)  The competition chair then assembles a team of
organizers, and distributes the work for the next edition of the
competition.
%
The SMT Workshop includes a block of time to present the competitors
and results of the competition.  The workshop is affiliated with a
major conference in the field of automated reasoning each year: with
CAV in 2015, with IJCAR in 2016, again with CAV in 2017, and with FLoC
in~2018.  Consequently, its date varies.  Competition results were
presented on July~19 in 2015, on July~2 in 2016, on July~23 in 2017,
and on July~13 in~2018.

@@

The competition rules are revised each year, and a (near final) draft
version of the rules is made public on the competition web site around
mid-April.  The competition chair has ultimate responsibility for the
rules, but changes are often preceded by discussions among the
organizers or within the SMT community.  Such discussions are
initiated by a Call for Comments that is sent out to the SMT-COMP
mailing list~\cite{smtcomp-mailinglist} in February or early March.
Publicly, this call is the first harbinger of a new edition of the SMT
Competition.

@@

All problems used in the SMT Competition come from the SMT Library
(SMT-LIB).  This is a large collection of benchmark problems from
various sources.  The SMT Library is available from a public
repository~\cite{smtlib-repository}, and each new release is mirrored
on StarExec, the cluster on which the competition runs.  Users of SMT
solvers are encouraged to submit new and interesting benchmarks to the
library, which has grown from 1,352 benchmarks in~2005~\cite{BdMS05}
to 347,011 benchmarks in 2018.

Benchmarks in the SMT Library are written in the SMT-LIB
language~\cite{BarFT-RR-17}, a text-based format that defines the
syntax and semantics of solver input and output.  This includes a
language for terms and formulas, and a command language for
interacting with SMT solvers.  For instance,
Figure~\ref{fig:smtlib-example} shows the example formula from
Section~\ref{sec:introduction} as a benchmark in SMT-LIB syntax, with
commands to the SMT solver typeset in bold.  In~2016, benchmarks were
updated from version~2.0 to version~2.5 of the SMT-LIB language.
Since~2017, benchmarks are written in version~2.6.  Fortunately,
versions~2.5 and~2.6 are largely backwards-compatible to 2.0, so that
older solvers are still able to compete with at most minor
modifications.

@@

Additionally, the SMT Library distinguishes between \emph{incremental}
and \emph{non-incremental} benchmarks.  Non-incremental benchmarks
contain a single {\tt check-sat} command, which instructs the SMT
solver to determine the satisfiability of the benchmark.  (Valid
solver responses are {\tt sat}, {\tt unsat}, and {\tt unknown}.)
Incremental benchmarks exercise additional solver features, such as
the ability to retract assertions, and typically contain multiple {\tt
  check-sat} commands.  These benchmarks originate from applications
such as bounded model checking~\cite{TODO}, where SMT solvers interact
with other tools in a feedback loop.

@@

The SMT Competition consists of several tracks.  The \emph{main
  track}, which has been a staple of the competition since its
inception in 2005, features non-incremental benchmarks.  The
\emph{application track}, which has been part of the competition since
2011~\cite{TODO}, features incremental benchmarks.  These benchmarks
are passed to each solver one command at a time by a trace executor,
which waits for the solver's response before passing the next
benchmark command (to prevent look-ahead behavior).  The
\emph{unsat-core track} uses main-track benchmarks that are known to
be unsatisfiable, and solvers are evaluated on their ability to find
small unsatisfiable cores (i.e., a small but still unsatisfiable
subset of the benchmark's assertions).  The unsat-core track had first
been part of the competition in 2012~\cite{TODO}, but was then
discontinued partly because of the competition's move to StarExec and
lacking tool support.  It was re-introduced as an experimental track
in 2016, and has been a regular competition track again since~2017.

@@

SMT Competitions until~2014 employed a pseudo-random selection process
to further cull the number of benchmarks used in the competition.
However, a 2013 evaluation of SMT-COMP and SMT-LIB found that this
``significantly lessens the ability of a competition to determine
`best' solvers.''~\cite{CSW15} rTogether with the increased
computational resources available to the competition since its move to
StarExec, this prompted a paradigm shift.  Since 2015, the competition
is evaluating all solvers on all eligible benchmarks. \TODO: benchmark
weights

@@

Jobs consist of individual \emph{job pairs}.  Each job pair
corresponds to a specific solver-benchmark combination.
Figure~\ref{fig:job-pairs} shows the total number of job pairs for the
SMT Competition from~2015 to~2018.  Over this period, the number has
grown by~72\,\%, from~1,028,615 job pairs in~2015 to~1,776,062 job
pairs in~2018.  (This is the number of unique solver-benchmark
combinations that were part of the competition.  The number of job
pairs that were actually run is even higher: test jobs and job pairs
that had to be re-run, e.g., because of issues with the StarExec
infrastructure, are not included.)  For comparison, the~2014
competition only ran~339,714 job pairs~\cite{CDW14}.

Also shown in Figure~\ref{fig:job-pairs} is the total wall-clock time
(summed over all job pairs) for the competition.  This has more than
doubled, from 3.5~years in~2015 to 7.6~years in~2018.  (These are
solver run-times only.  Time that the cluster spent on pre- and
post-processing of benchmarks and solver output or on other auxiliary
tasks is not included.)  The increase in~2016 is largely due to the
inclusion of non-incremental benchmarks with unknown status; these
were evaluated with a wall-clock time limit of 10~minutes.  In~2017,
when these benchmarks had become eligible for the main track,
main-track job pairs were first run with a time limit of 10~minutes;
when it became apparent to the organizers that there were sufficient
resources to increase this limit, job pairs that had timed out were
re-run with a time limit of 20~minutes.  Table~\ref{table:time-limits}
shows the wall-clock time limits that were imposed for each track and
year.

\begin{table}
  \caption{Wall-clock time limits}
  \label{table:time-limits}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
    & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    Main track        & 40~min & 40~min & 20~min & 20~min \\
    Application track & 40~min & 40~min & 40~min & 40~min \\
    Unsat-core track  &     -- & 40~min & 40~min & 40~min \\
    \hline
  \end{tabular}
\end{table}

@@

The StarExec infrastructure has been vitally important in allowing the
competition to grow to its current size.  The competition organizers
have given the StarExec developers comprehensive feedback, and filed
dozens of feature requests and bug reports since~2013.  The
infrastructure has become increasingly stable; serious issues are now
rare.  When they did surface during an ongoing competition, they
received a swift response by the StarExec team (under the lead of
Aaron Stump).  This has been critical to the success of the
competition on more than one occasion.

@@

Table~\ref{table:participants} lists the solvers that participated
between~2015 and~2018, together with their submitter(s) and
institutional affiliations (which may have changed over time).  Note
that most solvers were developed by a group of people; the table does
not list all contributors but only submitters.
%
Participants are also encouraged to submit a short system description
of their solver, including a list of its authors and an explanation of
the SMT solving approach used.  System descriptions are published on
the SMT-COMP website~\cite{smtcomp-web}.  They were submitted for
about 60\,\% of all solver versions since 2015.

\begin{table}
  \caption{Participants (2015--2018)}
  \label{table:participants}
  \centering
  \begin{tabular}{|l|p{13cm}|} %TODO: fix width
    \hline
    Solver & Submitters (Affiliations)\\
    \hline
    ABC [\TODO]       & Valeriy Balabanov
                        (Mentor Graphics)\\
    Alt-Ergo          & Albin Coquereau
                        (CNRS and University of Paris-Sud)\\
    AProVE            & Carsten Fuhs
                        (University College London; Birkbeck, University of London)\\
    Boolector         & Mathias Preiner
                        (Johannes Kepler University)\\
    COLIBRI           & Fran\c{c}ois Bobot
                        (French Alternative Energies and Atomic Energy Commission)\\
    Ctrl-Ergo         & Mohamed Iguernlala
                        (CNRS and University of Paris-Sud)\\
    CVC3              & Kshitij Bansal
                        (New York University)\\
    CVC4              & Kshitij Bansal, Clark Barrett, Andres N\"otzli, Duligur Ibeling
                        (New York University; Stanford University)\\
    MapleSTP          & Jimmy Liang
                        (University of Waterloo)\\
    MinkeyRink        & Trevor Hansen
                        (University of Melbourne)\\
    OpenSMT2          & Matteo Marescotti, Antti Hyv\"arinen
                        (University of Lugano)\\
    ProB              & Sebastian Krings
                        (University of D\"usseldorf)\\
    Q3B               & Martin Jon\'a\v{s}
                        (Masaryk University)\\
    raSAT             & Tung Vu Xuan
                        (Japan Advanced Institute of Science and Technology)\\
    Redlog            & Haniel Barbosa
                        (Inria Nancy)\\
    SMT-RAT           & Florian Corzilius, Gereon Kremer
                        (RWTH Aachen University)\\
    SMTInterpol       & J\"urgen Christ
                        (University of Freiburg)\\
    SPASS-SATT        & Martin Bromberger
                        (Max Planck Institute for Informatics)\\
    STP               & Mate Soos, Trevor Hansen, Norbert Manthey
                        (National University of Singapore; University of Melbourne; Amazon Web Services)\\
    toysmt            & Masahiro Sakai
                        (Toshiba Corporation)\\
    Vampire           & Giles Reger
                        (University of Manchester)\\
    veriT             & David D\'eharbe, Haniel Barbosa, Hans-J\"org Schurr
                        (Federal University of Rio Grande do Norte; Inria Nancy)\\
    XSat              & Martin Velez
                        (University of California, Davis)\\
    Yices2            & Bruno Dutertre, Dejan Jovanovi\'c
                        (SRI International)\\
    Z3                & Christoph Wintersteiger, Aleksandar Zelji\'c
                        (Microsoft Research; Uppsala University)\\
    \hline
  \end{tabular}
\end{table}

@@

\TODO: explain those aspects of the procedure that are required to
understand the results (e.g., time limits, scoring)

@@

@@

\section{FLoC Olympic Games}
\label{sec:floc}

In 2014, the SMT Competition was part of the FLoC Olympic Games.
These gave the competition increased visibility and sponsored three
Kurt G\"odel medals.  After substantial internal debate, the 2014
competition organizers decided to award these to the winner of the
main track's QF\_BV division (which has historically been the logic
with the largest number of solver submissions and job pairs), as well
as to the two best main-track solvers according to a competition-wide
ranking that had been instituted especially for this
purpose~\cite{DBLP:journals/jsat/CokDW14}.  This ranking emphasizes
breadth of solver participation---a solver participating in many
logics need not be the best in any one of them to rank highly.

The competition-wide ranking for the main track was retained and
refined after~2014.  A contentious issue with this ranking has been
the scoring of incorrect solver responses.  In the per-division
rankings, an incorrect response causes a solver to be ranked behind
all correct solvers~\cite{rules18}.  But the competition's main track
consists of many independent divisions.  To balance the strong
interest in correct solvers against the risk of stifling innovation,
the competition-wide ranking was revised in~2017 to use a fixed
numeric penalty for each division with incorrect responses.  The value
of this penalty is currently set so that entering a (possibly buggy)
solver that can solve all benchmarks into a division has a positive
expected score if the probability of a soundness bug in the solver is
below~$20\,\%$.

The 2018 edition of the competition was again part of the FLoC Olympic
Games, which sponsored seven medals.  The competition organizers
awarded these to the following solvers:
\begin{itemize}
\item The best three main-track solvers according to the
  competition-wide ranking (first place: CVC4, second place:
  Yices-2.6.0, third place: SMTInterpol);
\item the solver(s) that won the QF\_BV division in the main track
  (sequential ranking: Boolector, parallel ranking: Minkeyrink-MT);
\item the solver that won the most competitive divisions in the
  application track (Yices-2.6.0);
\item the solver that won the most competitive divisions in the
  unsat-core track (Yices-2.6.0).
\end{itemize}

In comparison to the competition-wide ranking for the main track, the
metric used for the application and unsat-core track---simply counting
the number of competitive divisions that a solver has won---was rather
unsophisticated.  Future editions of the competition should perhaps
refine this to use a ranking scheme that is more similar to the
main-track ranking, by weighing divisions according to their relative
importance, and also by rewarding good performance from solvers other
than division winners.  A difficulty in adapting the main-track
ranking for the other tracks is that each main-track benchmark is
worth one point (before weighing) if solved correctly, while
benchmarks in the application and unsat-core track are worth widely
varying numbers of points.  Moreover, in the unsat-core track, the
size of the smallest unsatisfiable core---and hence the number of
points attainable on any given benchmark---may not be known precisely.

@@

>>>>

For space reasons, the discussion in this paper is necessarily
limited.  Complete data about past competitions since 2015 (and partly
for earlier competitions) is available from the competition website,
\url{http://www.smtcomp.org}.  This includes detailed results for each
solver/benchmark combination, totaling nearly 6 million data records
(about 1.1~GB in CSV format).

@@

The competition is organized under the direction of the SMT Steering
Committee, which appoints the competition chair.  (This appointment
should happen ``within 30 days from the end of the current edition of
the SMT workshop''~\cite{smt-bylaws} but in practice has often
happened later.)  The competition chair then assembles a team of
organizers, and oversees the work for the next edition of the
competition.
%
The SMT Workshop includes a block of time to present the competitors
and results of the competition.  The workshop is affiliated with a
major conference in the field of automated reasoning each year: with
CAV in 2015, with IJCAR in 2016, again with CAV in 2017, and with FLoC
in~2018.  Consequently, its date varies.  Competition results were
presented on July~19 in 2015, on July~2 in 2016, on July~23 in 2017,
and on July~13 in~2018.

@@

The competition rules are revised each year, and a (near final) draft
version of the rules is made public on the competition website around
mid-April.  The competition chair has ultimate responsibility for the
rules, but changes are often preceded by discussions among the
organizers or within the SMT community.  Such discussions are
initiated by a Call for Comments that is sent out to the SMT-COMP
mailing list~\cite{smtcomp-mailinglist} in February or early March.
Publicly, this call is the first harbinger of a new edition of the SMT
Competition.

@@

All problems used in the SMT Competition come from the SMT Library
(SMT-LIB).  This is a large collection of benchmark problems from
various sources.  The SMT Library is available from a public
repository~\cite{smtlib-repository}, and each new release is mirrored
on StarExec.  Users of SMT solvers are encouraged to submit new and
interesting benchmarks to the library, which has grown from 1,352
benchmarks in~2005~\cite{BdMS05} to 347,011 benchmarks in 2018.

Benchmarks in the SMT Library are written in the SMT-LIB
language~\cite{BarFT-RR-17}, a text-based format that defines the
syntax and semantics of solver input and output.  This includes a
language for terms and formulas, and a command language for
interacting with SMT solvers.  For instance,
Figure~\ref{fig:smtlib-example} shows the example formula from
Section~\ref{sec:introduction} as a benchmark in SMT-LIB syntax, with
commands to the SMT solver typeset in bold.

In~2016, benchmarks were updated from version~2.0 to version~2.5 of
the SMT-LIB language.  Since~2017, benchmarks are written in
version~2.6.  Fortunately, versions~2.5 and~2.6 are largely
backwards-compatible to 2.0, so that older solvers are still able to
compete with at most minor modifications.

@@

Additionally, the SMT Library distinguishes between \emph{incremental}
and \emph{non-incremental} benchmarks.  Non-incremental benchmarks
contain a single {\tt check-sat} command, which instructs the SMT
solver to determine the satisfiability of the benchmark.  (Valid
solver responses are {\tt sat}, {\tt unsat}, and {\tt unknown}.)
Incremental benchmarks exercise additional solver features, such as
the ability to retract assertions, and typically contain multiple {\tt
  check-sat} commands.  These benchmarks originate from applications
such as bounded model
checking~\cite{Gunther:2014:IBS:2632362.2632374}, where SMT solvers
interact with other tools in a feedback loop.

@@

The SMT Competition consists of several tracks.  The \emph{main
  track}, which has been a staple of the competition since its
inception in 2005, features non-incremental benchmarks.  The
\emph{application track}, which has been part of the competition since
2011~\cite{BDdMOS13}, features incremental benchmarks.  These
benchmarks are passed to each solver one command at a time by a trace
executor, which waits for the solver's response before passing the
next benchmark command (to prevent look-ahead behavior).  The
\emph{unsat-core track} uses main-track benchmarks that are known to
be unsatisfiable, and solvers are evaluated on their ability to find
small unsatisfiable cores (i.e., a small but still unsatisfiable
subset of the benchmark's assertions).  The unsat-core track had first
been part of the competition in 2012~\cite{CGBD12}, but was then
discontinued partly because of the competition's move to StarExec and
lacking tool support.  It was re-introduced as an experimental track
in 2016, and has been a regular competition track again since~2017.

@@

SMT Competitions until~2014 employed a pseudo-random selection process
to further cull the number of benchmarks used in the competition.
However, a 2013 evaluation of SMT-COMP and SMT-LIB found that this
``significantly lessens the ability of a competition to determine
`best' solvers.''~\cite{CSW15} Together with the increased
computational resources available to the competition since its move to
StarExec, this prompted a paradigm shift.  Since 2015, the competition
is evaluating all solvers on all eligible benchmarks. \TODO: benchmark
weights

@@

Jobs consist of individual \emph{job pairs}.  Each job pair
corresponds to a specific solver/benchmark combination.
Figure~\ref{fig:job-pairs} shows the total number of job pairs for the
SMT Competition from~2015 to~2018.  Over this period, the number has
grown by~72\,\%, from~1,028,615 job pairs in~2015 to~1,776,062 job
pairs in~2018.  (This is the number of unique solver/benchmark
combinations that were part of the competition.  The number of job
pairs that were actually run is even higher: test jobs and job pairs
that had to be re-run, e.g., because of issues with the StarExec
infrastructure, are not included.)  For comparison, the~2014
competition only ran~339,714 job pairs~\cite{CDW14}.

Also shown in Figure~\ref{fig:job-pairs} is the total wall-clock time
(summed over all job pairs) for the competition.  This has more than
doubled, from 3.5~years in~2015 to 7.6~years in~2018.  (These are
solver run-times only.  Time that the cluster spent on pre- and
post-processing of benchmarks and solver output or on other auxiliary
tasks is not included.)  The increase in~2016 is largely due to the
inclusion of non-incremental benchmarks with unknown status; these
were evaluated with a wall-clock time limit of 10~minutes.  In~2017,
when these benchmarks had become eligible for the main track,
main-track job pairs were first run with a time limit of 10~minutes;
when it became apparent to the organizers that there were sufficient
resources to increase this limit, job pairs that had timed out were
re-run with a time limit of 20~minutes.  (In this way, about 2.9 years
of wall-clock time in 2017 were spent on job pairs that were then
re-run.  This time is not included in Figure~\ref{fig:job-pairs}.)
Table~\ref{table:time-limits} shows the wall-clock time limits that
were imposed on job pairs for each track and year.

\begin{table}
  \caption{Wall-clock time limits.}
  \label{table:time-limits}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
    & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    Main track        & 40~min & 40~min & 20~min\protect\footnotemark & 20~min \\
    Application track & 40~min & 40~min & 40~min\phantom{$^{1.}$} & 40~min \\
    Unsat-core track  &     -- & 40~min & 40~min\phantom{$^{1.}$} & 40~min \\
    \hline
  \end{tabular}
\end{table}
\footnotetext{These job pairs were first run with a time limit of
  10~minutes.  See the text for details.}

@@

@@

Table~\ref{table:participants} lists the solvers that participated
between~2015 and~2018, together with their submitter(s) and
institutional affiliations (which may have changed over time).  Note
that most solvers were developed by a group of people; the table does
not list all contributors but only submitters.
%
Participants are also encouraged to submit a short system description
of their solver, including a list of its authors and an explanation of
the SMT solving approach used.  System descriptions are published on
the SMT-COMP website.  They were submitted for about 60\,\% of all
solver versions since 2015.

\begin{table}
  \caption{Participants (2015--2018)}
  \label{table:participants}
  \centering
  \begin{tabular}{|l|p{11.7cm}|} %TODO: fix width
    \hline
    Solver & Submitters (Affiliations)\\
    \hline
    ABC~\cite{DBLP:conf/cav/BraytonM10} & Valeriy Balabanov
                        (Mentor Graphics)\\
    Alt-Ergo          & Albin Coquereau
                        (CNRS and University of Paris-Sud)\\
    AProVE~\cite{DBLP:conf/cade/GieslBEFFOPSSST14} & Carsten Fuhs
                        (University College London; Birkbeck, University of London)\\
    Boolector~\cite{DBLP:conf/cav/NiemetzPWB18} & Mathias Preiner
                        (Johannes Kepler University)\\
    COLIBRI~\cite{colibri} & Fran\c{c}ois Bobot
                        (French Alternative Energies and Atomic Energy Commission)\\
    Ctrl-Ergo~\cite{ctrl-ergo} & Mohamed Iguernlala
                        (CNRS and University of Paris-Sud)\\
    CVC3~\cite{cvc3}  & Kshitij Bansal
                        (New York University)\\
    CVC4~\cite{DBLP:conf/cav/BarrettCDHJKRT11}  & Kshitij Bansal, Clark Barrett, Andres N\"otzli, Duligur Ibeling
                        (New York University; Stanford University)\\
    MapleSTP~\cite{maplestp} & Jimmy Liang
                        (University of Waterloo)\\
    MinkeyRink~\cite{minkeyrink} & Trevor Hansen
                        (University of Melbourne)\\
    OpenSMT2~\cite{opensmt2} & Matteo Marescotti, Antti Hyv\"arinen
                        (University of Lugano)\\
    ProB~\cite{prob}  & Sebastian Krings
                        (University of D\"usseldorf)\\
    Q3B~\cite{q3b}    & Martin Jon\'a\v{s}
                        (Masaryk University)\\
    raSAT~\cite{rasat} & Tung Vu Xuan
                        (Japan Advanced Institute of Science and Technology)\\
    Redlog~\cite{redlog} & Haniel Barbosa
                        (Inria Nancy)\\
    SMT-RAT~\cite{smt-rat} & Florian Corzilius, Gereon Kremer
                        (RWTH Aachen University)\\
    SMTInterpol~\cite{} & J\"urgen Christ
                        (University of Freiburg)\\
    SPASS-SATT~\cite{} & Martin Bromberger
                        (Max Planck Institute for Informatics)\\
    STP~\cite{}        & Mate Soos, Trevor Hansen, Norbert Manthey
                        (National University of Singapore; University of Melbourne; Amazon Web Services)\\
    toysmt~\cite{}     & Masahiro Sakai
                        (Toshiba Corporation)\\
    Vampire~\cite{}    & Giles Reger
                        (University of Manchester)\\
    veriT~\cite{DBLP:conf/cade/BoutonODF09} & David D\'eharbe, Haniel Barbosa, Hans-J\"org Schurr
                        (Federal University of Rio Grande do Norte; Inria Nancy)\\
    XSat~\cite{}       & Martin Velez
                        (University of California, Davis)\\
    Yices2~\cite{}     & Bruno Dutertre, Dejan Jovanovi\'c
                        (SRI International)\\
    Z3~\cite{DBLP:conf/tacas/MouraB08} & Christoph Wintersteiger, Aleksandar Zelji\'c
                        (Microsoft Research; Uppsala University)\\
    \hline
  \end{tabular}
\end{table}

@@

\TODO: explain those aspects of the procedure that are required to
understand the results (e.g., scoring)

@@

\subsection{Division Rankings}
\label{sec:division-rankings}

@@

\subsection{Competition-Wide Ranking}
\label{sec:floc}

In 2014, the SMT Competition was part of the FLoC Olympic Games.
These gave the competition increased visibility and sponsored three
Kurt G\"odel medals.  After substantial internal debate, the 2014
competition organizers decided to award these to the winner of the
main track's QF\_BV division (which had historically been the logic
with the largest number of solver submissions and job pairs), as well
as to the two best main-track solvers according to a competition-wide
ranking that had been instituted especially for this
purpose~\cite{CDW14}.  This ranking emphasizes breadth of solver
participation---a solver participating in many logics need not be the
best in any one of them to rank highly.

The competition-wide ranking for the main track was retained and
refined after~2014.  Table~\ref{table:competition-wide-ranking} shows
the best three solvers according to this ranking for 2015--2018.  Also
shown is Z3, which ranked highly each year but was running hors
concours.  Sequential and parallel performance are reported
separately.
%
Note that scores are not directly comparable between different years:
the set of benchmarks changes from one year to the next, and also the
formula to compute the score changed (see below).  Moreover, readers
should keep in mind that this ranking---like any method that maps the
performance of solvers for a broad range of logics to a
one-dimensional value---is inherently limited.  We refer to the
individual division rankings (Section~\ref{sec:division-rankings}) for
more detailed information.

\begin{table}
  \caption{Competition-wide ranking for the main track: best solvers (by year).}
  \label{table:competition-wide-ranking}
  \centering
  \scalebox{.89}{\begin{tabular}{|c|p{2.2cm}|r|r|p{0cm}|c|p{2.2cm}|r|r|}
    \cline{1-4} \cline{6-9}
    \multicolumn{4}{|c|}{2015} & & \multicolumn{4}{c|}{2016} \\ \cline{1-4} \cline{6-9}
    Rank & Solver & Score  & Score  & & Rank & Solver & Score & Score \\
         &        & (sequential) & (parallel) & & & & (sequential) & (parallel) \\ \cline{1-4} \cline{6-9}
         & [Z3]              & 159.36 & 159.36 & &    & [Z3]   & 185.09 & 185.09 \\
      1. & CVC4              & 144.67 & 144.74 & & 1. & CVC4   & 180.95 & 181.19 \\
      2. & CVC4(exp)\footnotemark & 140.47 & 140.51 & & 2. & Yices2 & 119.29 & 119.29 \\
      3. & Yices             & 101.91 & 101.91 & & 3. & veriT  &  75.11 &  75.11 \\ \cline{1-4} \cline{6-9}
  \end{tabular}}

  \medskip

  \scalebox{.89}{\begin{tabular}{|c|p{2.2cm}|r|r|p{0cm}|c|p{2.2cm}|r|r|}
    \cline{1-4} \cline{6-9}
    \multicolumn{4}{|c|}{2017} & & \multicolumn{4}{c|}{2018} \\ \cline{1-4} \cline{6-9}
    Rank & Solver & Score  & Score  & & Rank & Solver & Score & Score \\
         &        & (sequential) & (parallel) & & & & (sequential) & (parallel) \\ \cline{1-4} \cline{6-9}
         & [Z3]        & 171.99 & 171.99 & & 1. & CVC4        & 211.99 & 211.99 \\
      1. & CVC4        & 161.38 & 161.76 & &    & [Z3]        & 186.19 & 186.19 \\
      2. & Yices2      & 110.63 & 110.63 & & 2. & Yices2      & 115.26 & 115.26 \\
      3. & SMTInterpol &  65.96 &  66.00 & & 3. & SMTInterpol &  65.32 &  65.38 \\ \cline{1-4} \cline{6-9}
  \end{tabular}}
\end{table}
\footnotetext{This was a distinct version of CVC4 that was designated as experimental.}

A contentious issue with this ranking has been the scoring of
incorrect solver responses.  In the division rankings, an incorrect
response causes a solver to be ranked behind all correct solvers for
that division.  But the competition's main track consists of many
independent divisions.  To balance the strong interest in correct
solvers against the risk of stifling innovation, the competition-wide
ranking was revised in~2017 to use a fixed numeric penalty for each
division with incorrect responses.  The value of this penalty is
currently set so that entering a (possibly buggy) solver that can
solve all benchmarks into a division has a positive expected score if
the probability of a soundness bug in the solver is
below~$20\,\%$.~\cite{rules18}

The 2018 edition of the competition was again part of the FLoC Olympic
Games, which sponsored seven medals.  The competition organizers
awarded these to the following solvers:
\begin{itemize}
\item The best three main-track solvers according to the
  competition-wide ranking (see
  Table~\ref{table:competition-wide-ranking}),
\item the solvers that won the QF\_BV division in the main track (see
  Table~\ref{TODO}),
  % TODO (sequential ranking: Boolector, parallel ranking: Minkeyrink-MT);
\item the solver that won the most competitive divisions in the
  application track (see Table~\ref{TODO}),
\item the solver that won the most competitive divisions in the
  unsat-core track (see Table~\ref{TODO}).
\end{itemize}

%TODO The latter two medals were won by Yices-2.6.0.

In comparison to the competition-wide ranking for the main track, the
metric used for the application and unsat-core track---simply counting
the number of competitive divisions that a solver has won---was rather
unsophisticated.  Future editions of the competition should perhaps
refine this to use a ranking scheme that is more similar to the
main-track ranking, by weighing divisions according to their relative
importance, and also by rewarding good performance from solvers other
than division winners.  A difficulty in adapting the main-track
ranking for the other tracks is that each main-track benchmark is
worth one point (before benchmark weights are applied) if solved
correctly, while benchmarks in the application and unsat-core track
are worth widely varying numbers of points.  Moreover, in the
unsat-core track, the size of the smallest unsatisfiable core---and
hence the number of points attainable on any given benchmark---may not
be known precisely.

\subsection{Improvement Over Time}

\subsection{Other Measures}

@@

The StarExec infrastructure has been vitally important in allowing the
competition to grow to its current size.  The competition organizers
have given the StarExec developers comprehensive feedback, and filed
dozens of feature requests and bug reports since~2013.  The
infrastructure has become increasingly stable; serious issues are now
rare.  When they did surface during ongoing competitions, they
received a swift response by the StarExec team (under the lead of
Aaron Stump).  This has been critical to the success of the
competition on more than one occasion.
